Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-08 edubots_surveys.Rnw
rev discussion - following paragraphs

One of the most interesting questions that can arise from the analysis of the
results, and that should require further study, is: Are teachers really aware
of the possibilities of chatbots in the classroom? The survey
only listed a few functionalities for the chatbots and just a few subjects selected
the option "Others". This may suggest  that most teachers did not really understand
at this point the actual potential of chatbots, since the responses listed were by no means exhaustive, and if the responders were more acquainted with the possibilities of the technology, possibly this response would have shown up many more times. Another way to look about it is
that, unless you provide the specific instructions on how to use a
tool, the teaching staff is already too busy or burn out to think about
innovation.

We can speculate that their opinions towards chatbots are informed by negative
experiences with customer support chatbots, which is what most people will have
experienced. This will probably require further study, but also will need to be
taken into account when introducing chatbot technologies in the classroom:
it will have to be as simple, and as satisfactory, as possible,
to (possibly) change this existing perception.

Regarding gender grouping, both genders agree in their uses, so it seems not
relevant at all. When looking at the plot containing the sector differentiation
it is interesting to observe how university teachers prefer in a higher
proportion to use them for grades and FAQs in comparison with other tertiary education teachers.
This seems reasonable as the frequency of seeing the students
is lower at the University so, an automatic tool for grade notification for
continuous evaluation seems more helpful.
Furthermore, the high student/teacher
ratios that university teachers have to deal with could be another reason to
have a higher number of them willing to use chatbots for FAQs. This could
ameliorate the number of misunderstandings and email overload that so many
students might generate.

>>>>

One of the most interesting questions arising from the analysis of the
results, and that should require further study, is: Are teachers really aware
of the possibilities of chatbots in the classroom? The survey
only listed a few functionalities for the chatbots, and just a few subjects selected
the option "Others". This may suggest that most teachers did not really understand
at this point the actual potential of chatbots, since the responses listed were by no means exhaustive. If the responders were more acquainted with the possibilities of this technology, this response would possibly have shown up many more times. Another way to look at it is that, unless you provide the specific instructions on how to use a
tool, the teaching staff is already too busy or burnt out to think about innovation.

We can speculate that teachers' opinions of chatbots are influenced by negative
experiences with customer support chatbots, which is what most people are likely to have
experienced. Further study may be needed to confirm this, but it is important to 
keep in mind when introducing chatbot technologies in the classroom.
To potentially change this existing perception, it will be necessary to make the chatbot as simple and satisfying to use as possible.

Regarding gender grouping, both genders agree in their uses, so it seems not
relevant at all. However, when we look at the plot containing the sector differentiation,
it is interesting to note that university teachers are more likely to use chatbots 
for grades and FAQs compared to other tertiary education teachers.
This seems reasonable as the frequency of seeing the students
is lower at the University so, an automatic tool for grade notification for
continuous evaluation would be more helpful.
Furthermore, the high student-to-teacher
ratios that university teachers often face could be another reason why
a higher number of them are willing to use chatbots for FAQs, as this could
reduce misunderstandings and email overload from students.
